ext_risk_copula

### 2019-02-15 ext_risk_copula.Rmd
fixed : ricker,hassell

#Ricker model :
```{r fig_ricker, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
library(abind)
rlist<-c(0,0.1,0.3,0.5,0.7,0.9,1.0,1.1,1.3,1.5,1.7,1.9) #rc = 1
numsims<-10000
numsteps<-25
numlocs<-5
K<-50
scl<-1
ext_thrs<-K/10
model<-"ricker"

@@

ricker_extrisk_d0<-data.frame(rlist,NA*numeric(length(rlist)),NA*numeric(length(rlist))) #initiate a dataframe to store ext risk at dispersal d=0 for all r
colnames(ricker_extrisk_d0)<-c("r","risk_left_d0","risk_right_d0")

@@

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
#pdf(paste(resloc,"ricker_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
#op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$avg_acf_left,s$avg_acf_right)

    res_ricker_local<-abind(res_ricker_local,temp_mat)

    ricker_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    ricker_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
    #plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
    #     panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    #lines(s$d_seq,s$risk_right,type="b",col="blue")
    #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
    #mtext(paste0("r = ", r))
}
#par(op)
#dev.off()
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","avgACF_left","avgACF_right")
dimnames(res_ricker_local)<-list(NULL,cnm,anm)

@@

res_ricker_global<-c()
# plot for global dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
#pdf(paste(resloc,"ricker_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
#op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$avg_acf_left,s$avg_acf_right)
    colnames(temp_mat)<-c("d","risk_left","risk_right","avgACF_left","avgACF_right")

    res_ricker_global<-abind(res_ricker_global,temp_mat)
    #plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
    #     panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    #lines(s$d_seq,s$risk_right,type="b",col="blue")
    #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    #mtext(paste0("r = ", r))
}
#par(op)
#dev.off()
```

@@

plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(0,2),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025left,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)

@@

```{r fig_hassell, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

@@

rlist<-seq(from=1.5,to=7.5,by=0.5)
numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-100
scl<-1
rc<-((b/(b-1)))^b # critical value of r from monotonic to osc steady state approach transition 
rlist<-sort(c(rlist,rc))

@@

# plot for local dispersal in D matrix 
pdf(paste(resloc,"hassell_ext_risk_local_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<- rlist[i]
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    hassell_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    hassell_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

saveRDS(hassell_extrisk_d0,paste(resloc,"hassell_extrisk_d0.RDS",sep=""))

# plot for local dispersal in D matrix 
pdf(paste(resloc,"hassell_ext_risk_global_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

@@

pdf("./Results/hassell/hassell_extrisk_d0.pdf",height = 6,width=6)
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.4,7.6),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)

>>>>

#Ricker model :
```{r sim_ricker, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
library(abind)
rlist<-c(0,0.1,0.3,0.5,0.7,0.9,1.0,1.1,1.3,1.5,1.7,1.9) #rc = 1
numsims<-10000
numsteps<-25
numlocs<-5
K<-50
scl<-1
ext_thrs<-K/10
model<-"ricker"

@@

#initiate a dataframe to store ext risk at dispersal d=0 for all r
ricker_extrisk_d0<-data.frame(rlist,NA*numeric(length(rlist)),NA*numeric(length(rlist))) 
colnames(ricker_extrisk_d0)<-c("r","risk_left_d0","risk_right_d0")

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right,s$noise_avg_acf_left,s$noise_avg_acf_right)
    res_ricker_local<-abind(res_ricker_local,temp_mat,along = 3)

    ricker_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    ricker_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right","noise_avg_acf_left","noise_avg_acf_right")
dimnames(res_ricker_local)<-list(NULL,cnm,anm)

@@

# For global dispersion
res_ricker_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right,s$noise_avg_acf_left,s$noise_avg_acf_right)
    res_ricker_global<-abind(res_ricker_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right","noise_avg_acf_left","noise_avg_acf_right")
dimnames(res_ricker_global)<-list(NULL,cnm,anm)
saveRDS(res_ricker_global,paste(resloc,"res_ricker_global.RDS",sep=""))
```

```{r fig_ricker, echo=F, results="hide",cache=T, cache.extra=list(seed,res_ricker_local,res_ricker_global)}
pdf(paste(resloc,"ricker_ext_risk_local_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

for(i in 1:dim(res_ricker_local)[3]){
  s<-res_ricker_local[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))

  ## Allow a second plot on the same graph
  par(new=TRUE)

  ylm2<-c(-0.04,0.04)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  lines(s$d, s$pop_avg_acf_right, col="skyblue")

  lines(s$d, s$noise_avg_acf_left, col="green")

  ## a little farther out (line=3.2) to make room for labels
  mtext("Avg. ACF",side=4,line=3.2,col="green4") 
  axis(4, ylim=ylm2, las=1,col="green4",col.axis="green4")
}
par(op)
dev.off()

pdf(paste(resloc,"ricker_ext_risk_global_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

for(i in 1:dim(res_ricker_global)[3]){
  s<-res_ricker_global[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))

  ## Allow a second plot on the same graph
  par(new=TRUE)

  ylm2<-c(-0.04,0.04)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  lines(s$d, s$pop_avg_acf_right, pch=16, col="skyblue")

  lines(s$d, s$noise_avg_acf_left, col="green")

  ## a little farther out (line=3.2) to make room for labels
  mtext("Avg. ACF",side=4,line=3.2,col="green4") 
  axis(4, ylim=ylm2, las=1,col="green4",col.axis="green4")
}
par(op)
dev.off()
```

@@

plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_left_d0,col="red",type="b",
     ylim=c(0,1),xlim = c(0,2),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025left,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975left,
       angle=90,length=0.1,col="red",code=3)
abline(v=1,lty="dotted") #rc=1

@@

```{r sim_hassell, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

@@

rlist<-seq(from=1.5,to=7.5,by=0.5)
numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-100
scl<-1
rc_hassell<-((b/(b-1)))^b # critical value of r from monotonic to osc steady state approach transition 
rlist<-sort(c(rlist,rc_hassell))

@@

res_hassell_local<-c()

for(i in c(1:length(rlist))){
    r<- rlist[i]
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right,s$noise_avg_acf_left,s$noise_avg_acf_right)
    res_hassell_local<-abind(res_hassell_local,temp_mat,along = 3)

    hassell_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    hassell_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right","noise_avg_acf_left","noise_avg_acf_right")
dimnames(res_hassell_local)<-list(NULL,cnm,anm)

saveRDS(hassell_extrisk_d0,paste(resloc,"hassell_extrisk_d0.RDS",sep=""))
saveRDS(res_hassell_local,paste(resloc,"res_hassell_local.RDS",sep=""))

# For global dispersion
res_hassell_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right,s$noise_avg_acf_left,s$noise_avg_acf_right)
    res_hassell_global<-abind(res_hassell_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right","noise_avg_acf_left","noise_avg_acf_right")
dimnames(res_hassell_global)<-list(NULL,cnm,anm)
saveRDS(res_hassell_global,paste(resloc,"res_hassell_global.RDS",sep=""))
```

```{r fig_hassell, echo=F, results="hide",cache=T, cache.extra=list(seed,res_hassell_local,res_hassell_global)}
pdf(paste(resloc,"hassell_ext_risk_local_disp.pdf",sep=""),height=9,width=18)
op<-par(mfrow=c(3,5),mar=c(5.2,4.2,1.2,6.2))

for(i in 1:dim(res_hassell_local)[3]){
  s<-res_hassell_local[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))

  ## Allow a second plot on the same graph
  par(new=TRUE)

  ylm2<-c(-0.04,0.04)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  lines(s$d, s$pop_avg_acf_right, col="skyblue")

  lines(s$d, s$noise_avg_acf_left, col="green")

  ## a little farther out (line=3.2) to make room for labels
  mtext("Avg. ACF",side=4,line=3.2,col="green4") 
  axis(4, ylim=ylm2, las=1,col="green4",col.axis="green4")
}
par(op)
dev.off()

pdf(paste(resloc,"hassell_ext_risk_global_disp.pdf",sep=""),height=9,width=18)
op<-par(mfrow=c(3,5),mar=c(5.2,4.2,1.2,6.2))

for(i in 1:dim(res_hassell_global)[3]){
  s<-res_hassell_global[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))

  ## Allow a second plot on the same graph
  par(new=TRUE)

  ylm2<-c(-0.04,0.04)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  lines(s$d, s$pop_avg_acf_right, col="skyblue")

  lines(s$d, s$noise_avg_acf_left, col="green")

  ## a little farther out (line=3.2) to make room for labels
  mtext("Avg. ACF",side=4,line=3.2,col="green4") 
  axis(4, ylim=ylm2, las=1,col="green4",col.axis="green4")
}
par(op)
dev.off()
```

@@

pdf("./Results/hassell/hassell_extrisk_d0.pdf",height = 6,width=6)
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.4,7.6),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted")
